### 2017-02-06 R/ITHIM.Rmd
Update to cambridge.Rmd

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = FALSE}
document("~/ITHIM/")
#install("~/ITHIM/")
install_github("syounkin/ITHIM", ref="devel")
install_github("smbache/magrittr", ref="master")

>>>>

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = FALSE}
document("~/ITHIM/")
#install("~/ITHIM/")
install_github("syounkin/ITHIM", ref="cambridge")
install_github("smbache/magrittr", ref="master")
